Really Good Title

### 2019-01-07 documentation/paper.tex
Curriculum learning

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/standard_5t.png}
\caption{Trained networks against all other bots.}
\label{fig:standard_5t_aa}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_1.png}
\caption{Trained networks against all other bots.}
\label{fig:self_adapt_1_aa}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_2_5t.png}
\caption{Trained networks against all other bots.}
\label{fig:self_adapt_1_5t_aa}
\end{figure}

We can see in figures \ref{self_adapt_1_5t} and \ref{self_adapt_1_5t_aa} that the results improve significantly in both cases. Self adaptation causes the networks trained on \texttt{_5t} opponents to get consistent results across the board.

\todo{trainer\_5t does not coincide on the two graphs, what happened? We get a good result against trainer_5t according to the bottom graph}

@@

We also explored a method similar to (5) in \cite{self_adapt}, where each parameter gets it's own mutation sigma parameter. This produces similar results to the harsh teachers with per-individual self adaptation

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_2.png}
\caption{Trained networks against all other bots.}
\label{fig:self_adapt_2_aa}
\end{figure}

\todo{similar to section before without 5t}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_2_5t.png}
\caption{Trained networks against all other bots.}
\label{fig:self_adapt_2_5t_aa}
\end{figure}

\todo{not very predictable behaviour}
\todo{works good for a few examples}
\todo{remember prof has never seen this stuff working and will be happy if it has disadvantages}

\section{Changing opponent}

200 gen \texttt{gintonicV9\_5t}, 200 gen \texttt{com\_11\_5t}, 200 gen \texttt{gintonicV9}, 200 gen \texttt{com\_11}.
\todo{argument with the previous plots that this is a good idea}
\todo{other ideas?}

\begin{figure}[H]
\center
\begin{tabular}{ccc}
standard & self adapt 1 & self adapt 2 \\
\includegraphics[width=0.3\textwidth]{img/standard_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} \\
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:changing opponent}
\end{figure}

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/change.png}
\caption{Trained networks against all other bots.}
\label{fig:change}
\end{figure}

\todo{only self adapt 1 works}
\todo{we could do more with more generations but loose the comparebility to the previous section}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.3\textwidth]{img/self_training_1.png}
\caption{Trained networks against all other bots.}
\label{fig:self_training_1}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_training_2.png}
\caption{Trained networks against all other bots.}
\label{fig:self_training_2}
\end{figure}

>>>>

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/standard_5t.png}
\caption{Best individuals against all bots.}
\label{fig:standard_5t_aa}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_1.png}
\caption{Best individuals against all bots.}
\label{fig:self_adapt_1_aa}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_2_5t.png}
\caption{Best individuals against all bots.}
\label{fig:self_adapt_1_5t_aa}
\end{figure}

We can see in figures \ref{fig:self_adapt_1_5t} and \ref{fig:self_adapt_1_5t_aa} that the results improve significantly in both cases. Self adaptation causes the networks trained on \texttt{\_5t} opponents to get consistent results across the board.

The surprisingly low performance against the easiest bot, \texttt{trainer\_5t} might be explained by the bot being too easy. The high initial fitness might encourage the survival of individuals with a low mutation rate, causing the algorithm to get stuck in a local optimum.

\todo{trainer5t does not coincide on the two graphs, what happened? We get a good result against trainer5t according to the bottom graph}

@@

We also explored a method similar to (5) in \cite{self_adapt}, where each parameter gets it's own mutation sigma parameter. This produces similar results to per-individual self adaptation with harsh teachers, but with benevolent teachers fails to reproduce the consistency of the other method.

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_2.png}
\caption{Best individuals against all bots.}
\label{fig:self_adapt_2_aa}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_2_5t.png}
\caption{Best individuals against all bots.}
\label{fig:self_adapt_2_5t_aa}
\end{figure}

\section{Curriculum learning}

We implemented a limited set of curriculum learning, where the training happens against increasingly harder opponents \texttt{gintonicV9\_5t}, \texttt{com\_11\_5t}, \texttt{gintonicV9}, and \texttt{com\_11} for 200 generations each. These bots previously worked as solid teachers. As can be seen on \ref{fig:change}, only the Per-individual self adaptation seems to work, there's no transfer of knowledge between the different bots for the other methods.

It's possible that with increasing the number of generations this algorithm would produce some advantages over training with just one teacher. Sadly, this would have to repeat all the previous experiments with a higher generation count for comparability's sake.

\begin{figure}[H]
\center
\begin{tabular}{ccc}
Standard & Per-individual s. a. & Per-parameter s. a. \\
\includegraphics[width=0.3\textwidth]{img/standard_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} \\
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:changing opponent}
\end{figure}

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/change.png}
\caption{Best individuals against all bots.}
\label{fig:change}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.3\textwidth]{img/self_training_1.png}
\caption{Best individuals against all bots.}
\label{fig:self_training_1}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_training_2.png}
\caption{Best individuals against all bots.}
\label{fig:self_training_2}
\end{figure}
